Assessing Digital Elevation Models with different image overlap using photogrammetry

### 2021-04-29 Draft.tex
Backup 20210429

% KAO: Remove extra spacing
\author{Robert van de Vlasakker}

% KAO: Remove extra newline
\address{} % Not needed

@@

% KAO: Use times symbol
\abstract{
Photogrammetry is easy to use these days and can be used to create a digital elevation models (DEM) of an area. 
Image overlap plays an important role in the process of photogrammetry.
A high overlap takes more time to gather in the field and takes longer to process.
Less overlap usually results in a less accurate calculations. 
In this paper the overlap of an area is artificially reduced and digital elevation models have been created with different image overlaps.
The digital elevation models (DEM) are compared to see how reducing the image overlap influences the result. 
When the absolute values of the DEM in compared large differences are visible.
However, when the scaled DEM's are compared in a boxplot the differences appear to be minimal.
Finally, violin plots have been made of the complete image set DEM minus the reduces image set DEM's.
The more images are used, the more the difference of the DEM's is centered around 0.
The DEM of the dataset with the highest images count seems to be the most similar to the DEM of the full dataset.
}

@@

Photogrammetry is the process of reconstructing spatial information with images through computer vision. 
These days most photogrammetry data is acquired with unmanned aerial vehicles (UAV) \citet{UAVAreMoreUsed}. 
UAV's come with GNSS and provide high resolution images needed for photogrammetry.
The process uses similar points visible on multiple images to determine the points in 3D space.
The reconstruction certainty of these points is strongly dependent on the overlap between different images. 
A digital elevation model (DEM) is a popular product from photogrammetry \citet{DemIncrease1}.
A DEM is a 2D grid containing height values and is frequently used in geoinformation applications.
It is therefore important to create high quality DEM's.

A higher image overlap results in more similar image points, which will increase the reconstruction certainty of the points \citep{MoreOverMoreAcc}.
A higher image overlap, does not automatically results in a denser point cloud. \citep{EffectofUABimgcamover}. 
A high overlap is needed in complex structures like vegetation; if parts of the object are not visible on the image, they will not be reconstructed in the point cloud \citep{AccessingImageOverlap}.
However, an image dataset with a high overlap takes longer to gather, and may results in multiple drone flights for a single dataset \citep{UAVpopularity}.
In the reconstruction process, a high overlap will also result in longer computation time \citep{AccessingImageOverlap}
By reducing the image overlap, time and computing power may be saved without loosing too much spatial information.
This main goal of this study is to investigate how different image overlap influence the DEM result that is created with photogrammetry.

>>>>

% KAO: Remove extra spacing
\author{Robert van de Vlasakker\textsuperscript{a}}

% KAO: Remove extra newline
\address{
    \textsuperscript{a}
    Wageningen University \& Research} % Not needed

@@

% KAO: Use times symbol
\abstract{
Photogrammetry is easy to use these days and can be used to create a digital elevation models (DEM) of an area. 
Image overlap plays an important role in the process of photogrammetry.
A high overlap takes more time to gather in the field and takes longer to process.
Less overlap usually results in a less accurate calculations. 
In this paper the overlap of an area is artificially reduced and digital elevation models have been created with different image overlaps.
The DEM's are compared to see how reducing the image overlap influences the result. 
When the absolute values of the DEM are compared large differences are visible.
However, when the scaled DEM's are compared in a boxplot the differences appear to be minimal.
Finally, violin plots have been made of the complete image set DEM minus the reduces image set DEM's.
The more images are used, the more the difference of the DEM's is centered around 0.
The DEM of the dataset with the highest images count seems to be the most similar to the DEM of the full dataset.
}

@@

Photogrammetry is the process of reconstructing spatial information with images through computer vision. 
These days most photogrammetry data is acquired with unmanned aerial vehicles (UAV) \citep{UAVAreMoreUsed}. 
UAV's come with GNSS and provide high resolution images needed for photogrammetry.
The process uses similar points visible on multiple images to determine the points in 3D space.
The reconstruction certainty of these points is strongly dependent on the overlap between different images. 
A digital elevation model (DEM) is a popular product from photogrammetry \citep{DemIncrease1}.
A DEM is a 2D grid containing height values and is frequently used in geoinformation applications.
It is therefore important to create high quality DEM's.

A higher image overlap results in more similar image points, which will increase the reconstruction certainty of the points \citep{MoreOverMoreAcc}.
A higher image overlap, does not automatically results in a denser point cloud. \citep{EffectofUABimgcamover}. 
A high overlap is needed in complex structures like vegetation; if parts of the object are not visible on the image, they will not be reconstructed in the point cloud \citep{AccessingImageOverlap}.
However, an image dataset with a high overlap takes longer to gather, and may require multiple drone flights for a single dataset \citep{uavpop}.
In the reconstruction process, a high overlap will also result in longer computation time \citep{AccessingImageOverlap}
By reducing the image overlap, time and computing power may be saved without loosing too much spatial information.
%The goal of this study is to investigate the results on the image processing results of using reduced image sets of the same area. 
This main goal of this study is to investigate how different image overlap influences the DEM result that is created with photogrammetry.
It will be investigated how the different image overlap influence the intermediate photogrammetry results and processing time.
